\section{Project description}

In this project, I would like to survey papers with topics related to human driving behavior recognition.

Intelligent vehicles is an interesting and popular topic. One distinguish example is Google's driverless car. Beyond designing autonomous cars, it would be more appealing if cars could be personalized.

What I mean by personalized is that a car could learn its drivers' preference through his behaviors, such as lane changing behaviors and speed adjusting behaviors,  during their driving so that later the car could serve the driver in a more customized fashion.

Although it may be true that driverless car, some day, would be widely adopted and no "human drivers" would exist anymore, we argue that people still have their own preferences on how a car should behave. For example, senior people may prefer lower driving speed compared to young drivers, cautious drivers tend to keep larger distance between cars. It would be ideal that driverless cars would take personal preferences into consideration when driving on road. Therefore, it is necessary to learn drivers' behaviors and  preferences.

In order to achieve the goal of obtaining and integrating drivers' preferences into driving assistance, a car needs to be trained by the driver to recognize his driving patterns and decision making preferences in order to be able to mimic or reproduce drivers' activities in the same situation. This requires a significant amount of machine learning.

There have been researches performed, but not limited to, in the following topics:

\begin{itemize}
\item{Security:}
    \begin{itemize}
    \item Human driving behavior could be learned to prevent car theft.
    \item Drunk drivers could be detected based on their driving behavior.
    \item Distraction detection could be identified based on drivers' behavior.
    \end{itemize}
\item{Intelligent driving:}
    \begin{itemize}
    \item Lane changing behavior could be modeled and used to make lane changing recommendation.
    \item Modeling drivers' preference on driving speed.
    \item Drivers' route preference is also being studied.
    \end{itemize}
\end{itemize}

I would like to proceed the project by doing a literature review on the methods and algorithms used to learn drivers' behavior and explore their applications.

A list of interesting papers are: \cite{4141877, 4298904, Buxton2003125, 4633642, 5, 6, Moeslund200690, 4142930, 1717363, 898310, 7, Kuge2000}
